---
title: "Practical-Machine-Learning-Cse-Prj"
author: "Martyn_Yap"
date: "Sunday, March 22, 2015"
output: html_document
---

## Reproduceablity

Loading the required libraries.
```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(RColorBrewer)
library(rattle)
library(randomForest)
```

Loading the same seed.
```{r}
set.seed(12345)
```

## Loading the data

Load the source files (aka data) *assumption that the working directory is setup
```{r}
training <- read.csv("source_files\pml-training.csv", na.strings=c("NA","#DIV/0!",""))
testing <- read.csv("source_files\pml-testing.csv, na.strings=c("NA","#DIV/0!",""))
```

##Partioning the training set into two

Partioning Training data set into two data sets, 60% for myTraining, 40% for myTesting:
```{r}
inTrain <- createDataPartition(y=training$classe, p=0.6, list=FALSE)
myTraining <- training[inTrain, ]; myTesting <- training[-inTrain, ]
dim(myTraining); dim(myTesting)
```

## Cleaning the data

```{r}
myDataNZV <- nearZeroVar(myTraining, saveMetrics=TRUE)
```

```{r}
myNZVvars <- names(myTraining) %in% c("new_window", "kurtosis_roll_belt", "kurtosis_picth_belt",
"kurtosis_yaw_belt", "skewness_roll_belt", "skewness_roll_belt.1", "skewness_yaw_belt",
"max_yaw_belt", "min_yaw_belt", "amplitude_yaw_belt", "avg_roll_arm", "stddev_roll_arm",
"var_roll_arm", "avg_pitch_arm", "stddev_pitch_arm", "var_pitch_arm", "avg_yaw_arm",
"stddev_yaw_arm", "var_yaw_arm", "kurtosis_roll_arm", "kurtosis_picth_arm",
"kurtosis_yaw_arm", "skewness_roll_arm", "skewness_pitch_arm", "skewness_yaw_arm",
"max_roll_arm", "min_roll_arm", "min_pitch_arm", "amplitude_roll_arm", "amplitude_pitch_arm",
"kurtosis_roll_dumbbell", "kurtosis_picth_dumbbell", "kurtosis_yaw_dumbbell", "skewness_roll_dumbbell",
"skewness_pitch_dumbbell", "skewness_yaw_dumbbell", "max_yaw_dumbbell", "min_yaw_dumbbell",
"amplitude_yaw_dumbbell", "kurtosis_roll_forearm", "kurtosis_picth_forearm", "kurtosis_yaw_forearm",
"skewness_roll_forearm", "skewness_pitch_forearm", "skewness_yaw_forearm", "max_roll_forearm",
"max_yaw_forearm", "min_roll_forearm", "min_yaw_forearm", "amplitude_roll_forearm",
"amplitude_yaw_forearm", "avg_roll_forearm", "stddev_roll_forearm", "var_roll_forearm",
"avg_pitch_forearm", "stddev_pitch_forearm", "var_pitch_forearm", "avg_yaw_forearm",
"stddev_yaw_forearm", "var_yaw_forearm")
myTraining <- myTraining[!myNZVvars]

myTraining <- myTraining[c(-1)]
```

```{r}
trainingV3 <- myTraining
for(i in 1:length(myTraining)) {
        if( sum( is.na( myTraining[, i] ) ) /nrow(myTraining) >= .6 ) {
		for(j in 1:length(trainingV3)) {
			if( length( grep(names(myTraining[i]), names(trainingV3)[j]) ) ==1)  {
				trainingV3 <- trainingV3[ , -j]
			}	
		} 
	}
}
myTraining <- trainingV3
rm(trainingV3)
```

```{r}
clean1 <- colnames(myTraining)
clean2 <- colnames(myTraining[, -58])
myTesting <- myTesting[clean1]
testing <- testing[clean2]
```

```{r}
for (i in 1:length(testing) ) {
        for(j in 1:length(myTraining)) {
		if( length( grep(names(myTraining[i]), names(testing)[j]) ) ==1)  {
			class(testing[j]) <- class(myTraining[i])
		}      
	}      
}
testing <- rbind(myTraining[2, -58] , testing) 
testing <- testing[-1,]
```

## Using Random Forests

```{r}
modFitB1 <- randomForest(classe ~. , data=myTraining)
```

## Generating files for submission.

```{r}
predictionsRF <- predict(modFitB1, testing, type = "class")
```

Function to generate files with predictions to submit for assignment
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id\problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(predictionsRF)
```